---
echo: false
warning: false
message: false
---

```{r}

# Import library
library(htmltools)

```


```{r}

# Source report custom functions
source("c_function.R")

```


```{r}

# Import and transform shape files
t_state_sf <- load_transform("data/state.shp")
t_road_sf  <- load_transform("data/road.shp")


```


<!------ Page container ------------------------------------------------------->
::: {.container .mx-3}

<!------ Top section ------------------------------------------------------->
::: {.top-section .mb-5}

<h3 class="page-title">Distribution of Major Roads Among Nigerian States</h3>


<!------ Grid ------------------------------------------------------->
::: {.grid}


::: {.g-col-12 .g-col-md-8}

<p class="text-summary">
Nigeria's vast territory is intricately woven together by an expansive network of major roads, stretching a
remarkable 68,926 kilometers in total. These roads encompass a hierarchy of connectivity: the trunk roads
uniting states, the primary roads linking local governments, and the secondary roads that seamlessly connect
towns and cities. This comprehensive overview visualization not only showcases the intricate web of roadways
that crisscross the nation but also provides a captivating breakdown of the total road length in kilometers for each individual state.
</p>

:::

::: {.g-col-12 .g-col-md-4}

```{r}

# Legend Container
tags$div(
  class = "legend-container",
  
  
  tags$div(
    class = "legend",
    
    tags$div(
      class = "title-icon",
      
      tags$h4(class = "title", "Legend"),
      tags$i(class = "bi bi-compass")
    ),
    
    tags$div(
      class = "text",
      tags$div(class = "pipe truck"),
      tags$h6("Trunk Road")
    ),
    
    tags$div(
      class = "text",
      tags$div(class = "pipe primary"),
      tags$h6("Primary Road")
    ),
    
    tags$div(
      class = "text",
      tags$div(class = "pipe secondary"),
      tags$h6("Secondary Road")
    )
  )
)

```

:::


:::
<!------ End Grid ------------------------------------------------------->

:::
<!------ End Top section --------------------------------------------------->




<!------ Charts Section ---------------------------------------------------->
::: {.grid .mb-3}


```{r}
#| output: asis

res <- purrr::map_chr(
  sort(t_state_sf$statename),
  
  \(state_name) {
    
    knitr::knit_child(
      text = c(
        "::: {.g-col-12 .g-col-md-4 .g-col-lg-3}",
        "",
        
        "```{r}",
        
        "temp <- create_outputs(state_capital_name = state_name)",
        
        "```",
        
        "<div class='sf-container'>",
        "<h4 class='title' data-bs-toogle='tooltip' data-bs-placement='top' title='State Name'>`r state_name`</h4>",
        "<h5 class='subtitle' data-bs-toogle='tooltip' data-bs-placement='top' title='Total Road Length'>`r temp$total_km`</h5>",
        
        "```{r}",
        
        "temp$plot",
        

        "```",
        
        "<div class='more-info-container'>",
        
        "<div class='content'>",
        
        "<p class='record'>Zone: <span class='zone'>`r temp$loc_zone`</span></p>",
        
        "<div class='horizontal-divider'></div>",
        
        "<div class='rec-row'><h6 class='title truck'>Truck:</h6><h6 class='value'>`r temp$Trunk`</h6></div>",
        "<div class='rec-row'><h6 class='title primary'>Primary:</h6><h6 class='value'>`r temp$Primary`</h6></div>",
        "<div class='rec-row'><h6 class='title secondary'>Secondary:</h6><h6 class='value'>`r temp$Secondary`</h6></div>",
        
        "</div>",
        
        "</div>",

        "</div>",
        
        
        ":::",
        ""
      ),
      envir = environment(),
      quiet = TRUE
    )
    
  }
)

cat(res, sep = "\n")

```


<!------ PDF Download ------------------------------------------------------>
::: {.g-col-12 .g-col-md-4 .g-col-lg-3}

```{r}

tags$div(
  class = "download-container",
  
  tags$div(
    class = "top",
    
    tags$i(class = "bi bi-star")
  ),
  
  tags$div(
    class = "middle",
    
    tags$i(class = "bi bi-file-earmark-pdf-fill"),
    
    tags$p(class = "label", "Major Road.pdf")
  ),
  
  tags$div(class = "horizontal-divider"),
  
  tags$div(
    class = "bottom",
    
    tags$div(
      class = "file-info",
      
      tags$h6("File size:"),
      tags$p("~ 493 KB")
    ),
    
    tags$a(
      download = "",
      href = "www/assets/roads.pdf",
      class = "dowload-btn", #btn-default
      
      tags$i(class = "bi bi-download")
    )
  )
)

```


:::
<!------ End of PDF Download ----------------------------------------------->

:::
<!------ End Charts Section ------------------------------------------------>


:::
<!------ End Page container --------------------------------------------------->



<!-------- Footer ------------------------------------------------------------->

::: {.mt-5}

```{r}

tags$div(
  class = "footer",
  
  tags$div(
    class = "f-column maintainer-add",
    
    tags$a(class = "github-text", "@Doh_Bams", href="https://github.com/dohbams"),
    tags$i(class = "bi bi-github")
  ),
  
  tags$div(class = "vertical-divider"),
  
  tags$div(
    class = "f-column r-library",
    
    tags$p(class = "r-text", "R"),
    tags$p(class = "text", "{ sf, tidyverse }")
  ),
  
  tags$div(class = "vertical-divider"),
  
  tags$div(
    class = "f-column data",
    
    tags$p(class = "data-title", "Data:"),
    tags$p(class = "text", "OSM, GRID3")
    
  )
)


```


:::
<!-------- End of Footer ------------------------------------------------------>


<!-------- JavaScript --------------------------------------------------------->
```{js}

$(document).ready(

  var tooltipTriggerList = [].slice.call(document.querySelectorAll('[data-bs-toggle="tooltip"]'));
  
  var tooltipList = tooltipTriggerList.map(function (tooltipTriggerEl) {
  
    return new bootstrap.Tooltip(tooltipTriggerEl);
    
  });
);

```





